
\iffalse
    \author{EE24BTECH11043}
    \section{ae}
    \chapter{2016}
\fi

	\item A single-stage gas turbine operates with an axial absolute flow at the entry and exit from the stage. The absolute flow angle at the nozzle exit is $70 \degree$. The turbine stage generates a specific work of $288 kJ/kg$ when operating with a mean blade speed of $440m/s$. The absolute velocity at the rotor entry is
		\begin{enumerate}
			\item $275.5 m/s$
			\item $551.5 m/s$
			\item $1103.0 m/s$
			\item $1654.5 m/s$
		\end{enumerate}
	\item An axial compressor operates such that is has an inlet and an exit total temparature of $300 K$ and $430 K$, respectiely. The isentropic efficency of the compressor is $85 \%$. If the ratio of specific heats is 1.4,then the total pressure ratio across the compressor is $\underline{\hspace{2cm}}$.
	\item The maximum value of coefficent of lift $\brak{C_1}$ for a 2D circular cylinder, provided at least one stagnation point lies on the cylinder surface, is predicted by the potential flow theory to be
		\begin{enumerate}
			\item $\pi/2$
			\item $\pi$
			\item $2\pi$
			\item $4\pi$
		\end{enumerate}
	\item The nozzle $\vec{AB}$, as shown below, leading to the test section of a low seed subsonic wind tunnel, has a contraction ratio of $10 : 1$. The pressure difference across the nozzle is maintained at $1000 N/m^2$ and the density of air is $1.23 kg/m^3$. Assuming one-dimensional, steady, inviscid flow, the velocity in the test section as measured at point $\vec{B}$ is $\underline{\hspace{1cm}} m/s$. \\
	\begin{figure}[!ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{circuitikz}
            \tikzstyle{every node}=[font=\normalsize]
            % Drawing the lines in the circuit
            \draw [short] (4.5,16.25) -- (10.25,15);
            \draw [short] (4.5,12) -- (10.25,13.5);
            \draw [dashed] (4.5,14.25) -- (10.25,14.25);
            
            % Adding labels for points A and B
            \node [font=\Large] at (4.25,14) {A};
            \node [font=\Large] at (10.5,14) {B};
            
            % Drawing an arrow with label for flow direction
            \draw [->, >=Stealth] (5.5,14.5) -- (8,14.5);
            \node [font=\normalsize] at (6.5,14.75) {Flow direction};
        \end{circuitikz}
    }
\end{figure}


	\item The rate of change of moment coefficient with respect to the angle of attack, $\frac{dC_m}{d\alpha}$, at half chord point of a thin airfoil, as per approximations from the thin airfoil theory is
		\begin{enumerate}
			\item $\pi^2/16$
			\item $\pi^2/12$
			\item $\pi^2/8$
			\item $\pi/2$
		\end{enumerate}
	\item A gaseous mixture of air and fuel enters a constant area combustion chamber at a velocity of $100 m/s$ and at a static temparature of $300 K$. The heat release due to combustion is $100 J/kgK$. The total temparature of air-fuel mixture after combustion is $\underline{\hspace{1 cm}} K$.
	\item Consider 1-D, steady, inviscid, compressible flow through a convergent nozzle. The total temparature and total pressure are $T_o$, $P_o$ respectively. The flow through the nozzle is choked with a mass flow rate of $m_o$. If the total temparature is increased to $4T_o$, with total pressure remaining unchanged, then the mass flow rate through the nozzle
		\begin{enumerate}
			\item remains unchanged.
			\item becomes half of $\dot{m}_o$.
			\item becomes twice of $\dot{m}_o$.
			\item becomes four times of $\dot{m}_o$.
		\end{enumerate}
	\item Consider a second order linear ordinary differential equation $\frac{d^2y}{dx^2}-4\frac{dy}{dx}+4y=0$, with the boundary conditions $y\brak{0};\frac{dy}{dx}\bigg|_{x=0}=1$. The value of $y$ at $x=1$ is
		\begin{enumerate}
			\item $0$
			\item $1$
			\item $e$
			\item $e^2$
		\end{enumerate}
	\item Consider the following system of lineal equatins: \\
		$2x-y+z=1$ \\
		$3x-3y+4z=6$ \\
		$x-2y+3z=4$ \\
		This system of linear equation has
		\begin{enumerate}
			\item no solution.
			\item one solution.
			\item two solutions.
			\item three solutions.
		\end{enumerate}
	\item A bar made of linear elastic isotropic material is fixed at one end and subjected to an axial force of $1 kN$ at the other end. The cross-sectional area of the bar is $100 mm^2$, length is $100 mm$ and the Young's Modulus is $1 \times 10^5 N/mm^2$. The strain energy stored in the bar is $\underline{\hspace{1cm}} Nmm$.
	\item A cantilever beam-spring system is shown in the figure, The beam is made with a material of Young's modulus $1 \times 10^5 N/mm^2$ and geometry such that its moment of inertia is $100 mm^4$ and length l=100 mm. It is supported by a spring of stiffness $K=30 N/mm$ and subjected to a load of $P=100N$ at the point '$\vec{B}$'. The deflection at the point '$\vec{B}$' due to the load P is $\underline{\hspace{1 cm}}mm$.
		\begin{figure}[!ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{circuitikz}
            \tikzstyle{every node}=[font=\normalsize]
            
            % Vertical line with ticks
            \draw [line width=0.6pt, short] (6.5,15.5) -- (6.5,13.25);
            \draw [short] (6.5,15.5) -- (6.25,15.25);
            \draw [short] (6.5,15) -- (6.25,14.75);
            \draw [short] (6.5,14.5) -- (6.25,14.25);
            \draw [short] (6.5,14) -- (6.25,13.75);
            \draw [short] (6.5,13.5) -- (6.25,13.25);
            
            % Horizontal lines and arrows
            \draw [line width=0.6pt, short] (6.5,15) -- (13.5,15);
            \draw [line width=0.6pt, short] (6.5,13.75) -- (13.5,13.75);
            \draw [line width=0.6pt, <->, >=Stealth] (6.5,13.5) -- (13.5,13.5);
            \draw [line width=0.6pt, ->, >=Stealth] (13.5,16) -- (13.5,14.25);
            
            % Zig-zag path
            \draw [line width=0.6pt, short] (13.5,14.25) -- (13.5,13);
            \draw [line width=0.6pt, short] (13.5,13) -- (13.25,12.75);
            \draw [line width=0.6pt, short] (13.25,12.75) -- (13.5,12.5);
            \draw [line width=0.6pt, short] (13.5,12.5) -- (13.25,12.25);
            \draw [line width=0.6pt, short] (13.25,12.25) -- (13.5,12);
            \draw [line width=0.6pt, short] (13.5,12) -- (13.25,11.75);
            \draw [line width=0.6pt, short] (13.25,11.75) -- (13.5,11.5);
            \draw [line width=0.6pt, short] (13.5,11.5) -- (13.5,11);
            
            % Horizontal base line
            \draw [line width=0.6pt, short] (12.75,11) -- (14.25,11);
            
            % Zig-zag at the base
            \draw [line width=0.6pt, short] (13.25,11) -- (12.75,10.5);
            \draw [line width=0.6pt, short] (13.5,11) -- (13,10.5);
            \draw [line width=0.6pt, short] (13.75,11) -- (13.25,10.5);
            \draw [line width=0.6pt, short] (14,11) -- (13.5,10.5);
            \draw [line width=0.6pt, short] (14.25,11) -- (13.75,10.5);
            \draw [line width=0.6pt, short] (13,11) -- (12.75,10.75);
            
            % Node labels
            \node [font=\large] at (7.25,15.5) {A};
            \node [font=\large] at (10.25,13.25) {I};
            \node [font=\large] at (13.5,16.25) {P};
            \node [font=\large] at (14,14.75) {B};
            \node [font=\normalsize] at (13.75,12.5) {K};
        \end{circuitikz}
    }
\end{figure}

	\item Determne the correctness or otherwise of the following statements, $\sbrak{a}$ and $\sbrak{r}$, \\
		$\sbrak{a}$: Ribs, used in airplane wings, increase the column buckling strength of the longitudinal stiffners. \\
		$\sbrak{r}$: Ribs distribute concentrated loads into the structure and redistribute stresses around discontinuities.
		\begin{enumerate}
			\item Both $\sbrak{a}$ and $\brak{r}$ are true and $\sbrak{r}$ is the correct reason for $\sbrak{a}$
			\item Both $\sbrak{a}$ and $\sbrak{r}$ are ture but $\sbrak{r}$ is not the correct reason for $\sbrak{a}$
			\item Both $\sbrak{a}$ and $\sbrak{r}$ are false
			\item $\sbrak{a}$ is true but $\sbrak{r}$ is false
		\end{enumerate}


