\iffalse
\title{GATE Questions 10}
\author{EE24BTECH11012 - Bhavanisankar G S}
\section{me}
\chapter{2014}
\fi
%\begin{enumerate}
	\item For the given assembly : 25 H7/g8, match Group A with Group B
		\begin{table}[h!]
\centering
\caption{Table 1}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Group A} & \textbf{Group B} \\
\hline
H & Shaft Type \\
\hline
IT8 & Hole type \\
\hline
IT7 & Hole Tolerance Grade \\
\hline
g & Shaft Tolerance Grade \\
\hline
\end{tabular}
\label{tab : Table 1}
\end{table}
		\begin{enumerate}
			\item P-I, Q-III, R-IV, S-II
			\item P-I, Q-IV, R-III, S-II
			\item P-II, Q-III, R-IV, S-I
			\item P-II, Q-IV, R-III, S-I
		\end{enumerate}
	\item If the Taylor's tool life exponent $n$ is 0.2, and the tool changing time is 1.5 min, then the tool life \brak{in min} for maximum production rate is
	\item An aluminium alloy $\brak{density 2600 kg/m^2}$ casting is to be produced. A cylindrical hole of 100 mm diameter and 100 mm length is made in the casting using sand core $\brak{density 1600 kg/m^3}$. The net buoyancy force \brak{in Newton} acting on the core is
	\item Choose the most appropriate word from the options below to complete the following sentence. \\
		Communication and interpersonal skills are (blank) important in their own ways.
		\begin{enumerate}
				\begin{multicols}{4}
			\item each
			\item both
			\item all
			\item either
				\end{multicols}
		\end{enumerate}
	\item Which of the options given below best completes the follwoing sentence ? \\
		She will feel much better if she (blank) .
		\begin{enumerate}
				\begin{multicols}{2}
				\item will get some rest
				\item gets some rest
				\item will be getting some rest
				\item is getting some rest
				\end{multicols}
		\end{enumerate}
	\item Choose the most appropriate pair of words from the options given below to complete the following sentence. \\
		She could not (blank) the thought of (blank) the election to her bitter rival.
		\begin{enumerate}
				\begin{multicols}{2}
				\item bear, loosing
				\item bare, loosing
				\item bear, losing
				\item bare, losing
				\end{multicols}
		\end{enumerate}
	\item A regular die has six sides with numbers 1 to 6 marked on its sides. If a very large number of throws shown the following frequencies of occurence 
		$$ 1 \rightarrow 0.167 ; 2 \rightarrow 0.167 ; 3 \rightarrow 0.152 $$
		$$ 4 \rightarrow 0.166 ; 5 \rightarrow 0.168 ; 6 \rightarrow 0.180 $$
		We call this die as
		\begin{enumerate}
				\begin{multicols}{4}
				\item irregular
				\item biased
				\item Gaussian
				\item insufficient
				\end{multicols}
		\end{enumerate}
	\item Fill in the missing number in the series \\
		2 \quad 3 \quad 6 \quad 15 \quad (blank) \quad 157.5 \quad 630
	\item Find the odd one in the following group \\
		Q,W,Z,B		B,H,K,M	\\
		W,C,G,J		M,S,V,X \\
		\begin{enumerate}
				\begin{multicols}{4}
				\item Q,W,Z,B
				\item B,H,K,M
				\item W,C,G,J
				\item M,S,V,X
				\end{multicols}
		\end{enumerate}
	\item Light of four colors ( red, blue, green, yellow ) are hung on a ladder. On every step of the ladder, there are two lights. If one of the lights is red, the other light on that step will always be blue. If one of the lights on a step is green, the other light on thats step will always be yellow. Which of the following statements is not necessarily correct ?
		\begin{enumerate}
			\item The number of red lights is equal to the number of blue lights.
			\item The number of green lights is equal to the number of yellow lights.
			\item The sum of the red and green lights is equal to the sum of the yellow and blue lights.
			\item The sum of the red and blue lights is equal to the sum of the green and yellow lights.
		\end{enumerate}
	\item The sum of eight consecutive odd numbers is 656. The average of four consecutive even numbers is 87. What is the sum of the smallest odd number and second largest even number ?
	\item The total exports and revenues from the exports of a country are given in the two charts shown below. The pie chart for exports shows the quantity of each item exported as a percentage of the total quantity of exports. The pie chart for the revenues shows the percentage of the total revenue generated through export of each item. The total quantity of exports of all the items is 500 thousand tonnes and the tonnes and the total revenues are 250 crore rupees. Which item among the following has generated the maximum revenue per kg ?
		\begin{figure}
			\centering
			\begin{circuitikz}
\tikzstyle{every node}=[font=\small]
\draw  (4.75,12.25) circle (3.25cm);
\draw (4.5,15.5) to[short] (4.5,9);
\draw [short] (4.5,12.25) -- (6.75,14.75);
\draw [short] (4.5,12.25) -- (7.5,10.5);
\draw [short] (4.5,12.25) -- (2,10.25);
\draw [short] (4.5,12.25) -- (1.75,13.5);
\node [font=\LARGE] at (4.5,16) {\textbf{EXPORTS}};
\node [font=\small] at (5.25,14) {Item 1};
\node [font=\small] at (6.5,12.5) {Item 2};
\node [font=\small] at (5.5,10.5) {Item 3};
\node [font=\small] at (3.5,10.5) {Item 4};
\node [font=\small] at (2.5,12) {Item 5};
\node [font=\small] at (3.5,13.75) {Item 6};
\node [font=\small] at (5,13.75) {11 \%};
\node [font=\small] at (6.5,12.25) {20 \%};
\node [font=\small] at (5.5,10.25) {19 \%};
\node [font=\small] at (3.5,10.25) {22 \%};
\node [font=\small] at (2.5,11.75) {12 \%};
\node [font=\small] at (3.5,13.5) {16 \%};
\end{circuitikz}
			\caption{}
			\label{25}
		\end{figure}
		\begin{figure}
			\centering
			\begin{circuitikz}
\tikzstyle{every node}=[font=\LARGE]
\draw  (4.75,12.25) circle (3.25cm);
\draw (4.5,15.5) to[short] (4.5,9);
\draw [short] (4.5,12.25) -- (6.75,14.75);
\draw [short] (4.5,12.25) -- (7.5,10.5);
\draw [short] (4.5,12.25) -- (2,10.25);
\draw [short] (4.5,12.25) -- (1.75,13.5);
\node [font=\small] at (5.25,14) {Item 1};
\node [font=\small] at (6.5,12.5) {Item 2};
\node [font=\small] at (5.5,10.5) {Item 3};
\node [font=\small] at (3.5,10.5) {Item 4};
\node [font=\small] at (2.5,12) {Item 5};
\node [font=\small] at (3.5,13.75) {Item 6};
\node [font=\small] at (5.25,13.5) {12 \%};
\node [font=\small] at (6.5,12.25) {20 \%};
\node [font=\small] at (5.75,10.25) {23 \%};
\node [font=\small] at (3.5,10) {6 \%};
\node [font=\small] at (2.5,11.75) {20 \%};
\node [font=\small] at (3.75,13.5) {19 \%};
\node [font=\LARGE] at (4.5,16.25) {\textbf{REVENUES}};
\end{circuitikz}
			\caption{}
			\label{25}
		\end{figure}
		\begin{enumerate}
				\begin{multicols}{4}
				\item Item 2
				\item Item 3
				\item Item 6
				\item Item 5
				\end{multicols}
		\end{enumerate}
	\item It takes 30 minutes to empty a half-full tank by draining it at a constant rate. It is decided to simultaneously pump water into the half-fulll tank while draining it. What is the rate at which water has to be pumped in so that it gets fully filled in 10 minutes ?
		\begin{enumerate}
				\begin{multicols}{2}
				\item 4 times the draining rate
				\item 3 times the draining rate
				\item 2.5 times the draining rate
				\item 2 times the draining rate
				\end{multicols}
		\end{enumerate}

