\iffalse
\chapter{2018}
\author{AI24BTECH11012}
\section{ee}
\fi

    \item In the logic circuit shown in the figure, Y is given by
    \input{figs/figs3/circuit1.tex}
    \begin{enumerate}
    \item Y=ABCD
    \item Y=(A+B)(C+D)
    \item Y=A+B+C+D
    \item Y=AB+CD
    \end{enumerate}
    
    \item The op-amp shown in the figure is ideal. The input impedance $\frac{v_{in}}{i_{in}}$ is given by
    \input{figs/figs3/circuit2.tex}
    \begin{enumerate}
    \item Z$\frac{R_1}{R_2}$
    \item -Z$\frac{R_2}{R_1}$
    \item Z
    \item -Z$\frac{R_1}{R_1+R_2}$
    \end{enumerate}
    
    \item A continuous-time input signal $x{t}$ is an eigenfunction of an LTI system, if the output is
    \begin{enumerate}
    \item $kx{t}$, where $k$ is an eigenvalue
    \item $ke^{iwt}x(t)$ where $k$ is an eigenvalue and $e^{iwt}$ is a complex exponential signal
    \item $x(t)e^{iwt}$, where $e^{iwt}$ is a complex signal
    \item $kH(w)$, where $k$ is an eigenvalue and $H(w)$ is a frequency response of the system
    \end{enumerate}
    
    \item Consider a non-singular $2x2$ square matrix $\vec{A}$. If $trace(\vec{A})=4$ and $trace{\vec{A}^2}=5$, the determinant of the matrix $\vec{A}$ is \rule{2.5cm}{0.4pt}(up to 1 decimal place).
    
    \item Let $f$ be a real-valued function of a real variable defined as $f(x)=x-[x]$, where $[x]$ denoted the largest integer less than or equal to $x$. The value of $\int_{0.25}^{1.25} f(x)dx$ is \rule{2cm}{0.4pt}(up to 2 decimal places).
    
    \item In the two-port network shown, the $h_{11}$ parameter (where, $h_{11}=\frac{V_1}{I_1}$, when $V_2=0$) in ohms is \rule{2.5cm}{0.4pt}(up to 2 decimal places).
    \input{figs/figs3/circuit3.tex}
    
    \item The series impedance matrix of a short three-phase transmission line in phase coordinates
$
\begin{bmatrix}
Z_s & Z_m & Z_m \\
Z_m & Z_s & Z_m \\
Z_m & Z_m & Z_s 
\end{bmatrix}
$
is given. If the positive sequence impedance is $ (1 + j10) \Omega $, and the zero sequence impedance is $ (4 + j31) \Omega$, then the imaginary part of $ Z_m $ (in $ \Omega $) is \rule{2.5cm}{0.4pt} (up to 2 decimal places).

\item The positive, negative and zero sequence impedances of a 125 MVA, three-phase, 15.5 kV, star-grounded, 50 Hz generator are $ j0.1 $ pu, $ j0.05 $ pu, and $ j0.01 $ pu respectively on the machine rating base. The machine is unloaded and working at the rated terminal voltage. If the grounding impedance of the generator is $ j0.01 $ pu, then the magnitude of fault current for a $ b $-phase to ground fault (in kA) is \rule{2cm}{0.4pt} (up to 2 decimal places).

\item A $ 1000 \times 1000$ bus admittance matrix for an electric power system has 8000 non-zero elements. The minimum number of branches (transmission lines and transformers) in this system are \rule{2cm}{0.4pt}(up to 2 decimal places).

\item The waveform of the current drawn by a semi-converter from a sinusoidal AC voltage source is shown in the figure. If $I_o=20$A, the rms value of fundamental component of the current is \rule{2cm}{0.4pt}A(up to 2 decimal places).
\input{figs/figs3/circuit4.tex}

\item A separately excited dc motor has an armature resistance $R_a=0.05\ohm$. The field excitation is kept constant. At an armature voltage of 100V, the motor produces a torque of 500 Nm at zero speed. Neglecting all mechanical losses, the no-load speed of the motor(in radian/s) for an armature voltage of 150 V is \rule{2cm}{0.4pt}(up to 2 decimal places).

\item Consider a unity feedback system with forward transfer function given by 
\[
G(s)=\frac{1}{\brak{s+1}\brak{s+2}}
\]
The steady-state error in the output of the system for a unit-step input is \rule{2cm}{0.4pt} (up to 2 decimal places).

\item A transformer with toroidal core of permeabiltiy $\mu$ is shown in the figure. Assuming uniform flux density across the circular core cross-section of radius $r<R$, and neglecting any leakage flux, the best estimate for the mean radius $R$ is

\input{figs/figs3/circuit5.tex}
\begin{enumerate}
\item $\frac{\mu Vr^2N_p^2w}{I}$
\item $\frac{\mu Ir^2N_pN_sw}{V}$
\item $\frac{\mu Vr^2N_p^2w}{2I}$
\item $\frac{\mu Ir^2N_p^2w}{2V}$
\end{enumerate}


