\iffalse	
	\chapter{2011}
	\author{AI24BTECH11016}
	\section{me}
\fi
\item
	Eigenvalues of a real symmetric matrix are always
		\begin{enumerate}
			\item positive
			\item negative
			\item real
			\item complex
		\end{enumerate}
	\item
	A pipe of $25 mm$ outer diameter carries steam. The heat transfer coefficient between the cylinder and surroundings is $5 W/m^{2}K$. It is proposed to reduce the heat loss from the pipe by adding insulation having a thermal conductivity of $0.05 W/mK$. Which one of the following statements is TRUE?
		\begin{enumerate}
			\item The outer radius of the pipe is equal to the critical radius.
			\item The outer radius of the pipe is less than the critical radius.
			\item Adding the insulation will reduce the heat loss
			\item Adding the insulation will increase the heat loss
		\end{enumerate}
	\item
	The contents of a well-insulated tank are heated by a resistor of $23 \ohm$ in which $10 A$ current is flowing. Consider the tank along with its contents as a thermodynamic system. The work done by the system and the heat transfer to the system are positive. The rates of heat ($Q$), work ($W$) and change in internal energy ($\Delta U$) during the process in $kW$ are
		\begin{enumerate}	
			\item $Q=0$, $W=-2.3$, $\Delta U = +2.3$
			\item $Q=+2.3$, $W=0$, $\Delta U = +2.3$
			\item $Q=-2.3$, $W=0$, $\Delta U = -2.3$
			\item $Q=0$, $W=+2.3$, $\Delta U = -2.3$
		\end{enumerate}
	\item
	Match the following criteria of material failure, under biaxial stresses $\sigma_{1}$ and $\sigma_{2}$ and yield stress $\sigma_{y}$, with their corresponding graphic representations:

    		\input{tables/ME2011/table.tex} 

	
	\item
	The product of two complex numbers $1+i$ and $2-5i$ is
		\begin{enumerate}
			\item $7-3i$
			\item $3-4i$
			\item $-3-4i$
			\item $7+3i$
		\end{enumerate}
	\item
	Cars arrive at a service station according to Poisson's distribution with a mean rate of 5 per hour. The service time per car is exponential with a mean of 10 minutes. At steady state, the average waiting time in the queue is
		\begin{enumerate}
			\item 10 minutes
			\item 20 minutes
			\item 25 minutes
			\item 50 minutes
		\end{enumerate}
	\item
	The word kanban is most appropriately associated with
		\begin{enumerate}
			\item economic order quantity
			\item just-in-time production
			\item capacity planning
			\item product design
		\end{enumerate}
	\item
	If $f\brak{x}$ is an even function and $a$ is a positive real number, then $\int_{-a}^{a} f\brak{x} dx$ equals
		\begin{enumerate}
			\item 0
			\item $a$
			\item $2a$
			\item $2 \int_{0}^{a} f\brak{x} dx$
		\end{enumerate}
	\item
	The coefficient of restitution of a perfectly plastic impact is
		\begin{enumerate}
			\item 0
			\item 1
			\item 2
			\item $\infty$
		\end{enumerate}
	A thin cylinder of inner radius $500 mm$ and thickness $10 mm$ is subjected to an internal pressure of $5 MPa$. The average circumferential (hoop) stress in $MPa$ is
		\begin{enumerate}
			\item 100
			\item 250
			\item 500
			\item 1000
		\end{enumerate}
	\item
	Which one among the following welding processes uses non-consumable electrode?
		\begin{enumerate}
			\item Gas metal arc welding
			\item Submerged arc welding
			\item Gas tungsten arc welding
			\item Flux coated arc welding
		\end{enumerate}
	\item
	The crystal structure of austenite is
		\begin{enumerate}
			\item body centered cubic
			\item face centered cubic
			\item hexagonal closed packed
			\item body centered tetragonal
		\end{enumerate}
\end{enumerate}

		Q.26 to Q.55 carry two marks each.
\begin{enumerate}
	\item
	A torque $T$ is applied at the free end of a stepped rod of circular cross-sections as shown in the figure. The shear modulus of the material of the rod is $G$. The expression for $d$ to produce an angular twist $\theta$ at the free end is
	
    		\input{figs/ME2011/figs3.tex}
    		
	
	\begin{enumerate}
		\item $\left(\frac{32TL}{\pi\theta G}\right)^{\frac{1}{4}}$
		\item $\left(\frac{18TL}{\pi\theta G}\right)^{\frac{1}{4}}$
		\item $\left(\frac{16TL}{\pi\theta G}\right)^{\frac{1}{4}}$
		\item $\left(\frac{2TL}{\pi\theta G}\right)^{\frac{1}{4}}$
	\end{enumerate}


